---
title: "Growth Rates of Algae"
output: rmarkdown::github_document
always_allow_html: yes
---

```{r, message=FALSE}
library(ggplot2)
library(ggthemr)
library(dplyr)
```

Read the dataset and convert the temperature and light intensity (lux) columns to factors.

```{r, echo=FALSE}
algae <- read.csv("C:/Users/Jutta/OneDrive/dataviz battle/algae/algae.csv", sep=";")
algae$temp <- as.factor(algae$temp)
algae$lux <- as.factor(algae$lux)
```

```{r, eval=FALSE}
algae <- read.csv("/algae/algae.csv", sep=";")
algae$temp <- as.factor(algae$temp)
algae$lux <- as.factor(algae$lux)
```

## Exploring the dataset

The dataset is available at [http://www.aquatext.com/tables/algaegrwth.htm](http://www.aquatext.com/tables/algaegrwth.htm). It contains specific growth rates of algae measured in divisions per day at different light intensities and temperatures.

```{r}
str(algae)
```

There are nineteen species of algae, each measured at four different temperatures (5, 10, 25, 30 °C) and two different light intensities (2500 and 5000 lux). The names of the nineteen species are

```{r}
levels(algae$species)
```

A summary of the growth rates by species:

```{r}
algae %>% group_by(species) %>% summarise(
  mean = mean(value),
  sd = sd(value),
  min = min(value),
  max = max(value)
  )
```

Now plot the growth rates for each species, lux and temperature:

```{r, warning=FALSE, fig.height=8, fig.width=9, dpi=400}
# set ggthemr "dust"
ggthemr("dust")

ggplot(algae, aes(x=temp, y=value, color=lux, group=lux)) +
  geom_point(size=2) +
  geom_line(size=1) + 
  facet_wrap( ~ species, nrow = 6) +
  labs(
    x = "Temperature (?C)", 
    y = "Divisions per day",
    color = "Light intensity (lux)") +
  ggtitle("Growth Rates of Algae") +
  theme(legend.position = "bottom", legend.direction = "horizontal")
```



